A comparative risk assesment of U.S. regional active transport using the ITHIM model

### 2016-09-27 R/ITHIM.Rmd
Created figure for California comparison

```{r newMETs, echo = TRUE, eval = TRUE, echo = FALSE}
newMETsFile <- "~/GHI/data/ATUS/ATUS_to_METS_key.csv"
newMETs <- read.csv(file = newMETsFile, stringsAsFactors = FALSE, colClasses = c("character","character","character","character","numeric","character","character","character"))
dataColumns <- c(1,5)
D <- newMETs[,dataColumns]
metaData <- newMETs[,-dataColumns]
newMETs <- list(Data = D, metaData = metaData)
activityCode <- ifelse(nchar(newMETs$Data$X6.digit.activity.code)==5,paste0("t0",newMETs$Data$X6.digit.activity.code),paste0("t",newMETs$Data$X6.digit.activity.code))

@@

```{r readnewMETs, echo = TRUE, eval = TRUE, echo = FALSE}
cpsFile <- "~/GHI/data/ATUS/atuscps_0311.dat"
cps <- read.table(cpsFile, header=T, skip=0, sep="," )
cps <- within(cps, {
    TUCASEID <- as.character(TUCASEID)
    TULINENO <- as.character(TULINENO)
    GEREG <- as.factor(GEREG)
    })
cps <- subset(cps, TULINENO == "1")

@@

```{r metKey, echo = TRUE, eval = TRUE, echo = FALSE}
allActivities <- colnames(summaryList$Data)
nonTravelActivities <- rownames(newMETs$metaData)[which(newMETs$metaData$Travel.related..Y.N. == "N")]
nonTravelActivities <- nonTravelActivities[which(nonTravelActivities %in% allActivities)]

@@

```{r parameters, eval = TRUE, echo = FALSE}
parameters <- ddply(D, .(SEX, AGECAT), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             )

@@

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = FALSE, warning = FALSE}
upper <- 100
length <- 100

@@

D <- within(D,{
  State <- factor(State, levels = c("NC","TX","VA","FL","AZ","NY","CA","Natl."))
})

@@

```
# Appendix

>>>>

```{r newMETs, echo = TRUE, eval = FALSE, echo = FALSE}
newMETsFile <- "~/GHI/data/ATUS/ATUS_to_METS_key.csv"
newMETs <- read.csv(file = newMETsFile, stringsAsFactors = FALSE, colClasses = c("character","character","character","character","numeric","character","character","character"))
dataColumns <- c(1,5)
D <- newMETs[,dataColumns]
metaData <- newMETs[,-dataColumns]
newMETs <- list(Data = D, metaData = metaData)
activityCode <- ifelse(nchar(newMETs$Data$X6.digit.activity.code)==5,paste0("t0",newMETs$Data$X6.digit.activity.code),paste0("t",newMETs$Data$X6.digit.activity.code))

@@

```{r readnewMETs, echo = TRUE, eval = FALSE, echo = FALSE}
cpsFile <- "~/GHI/data/ATUS/atuscps_0311.dat"
cps <- read.table(cpsFile, header=T, skip=0, sep="," )
cps <- within(cps, {
    TUCASEID <- as.character(TUCASEID)
    TULINENO <- as.character(TULINENO)
    GEREG <- as.factor(GEREG)
    })
cps <- subset(cps, TULINENO == "1")

@@

```{r metKey, echo = TRUE, eval = FALSE, echo = FALSE}
allActivities <- colnames(summaryList$Data)
nonTravelActivities <- rownames(newMETs$metaData)[which(newMETs$metaData$Travel.related..Y.N. == "N")]
nonTravelActivities <- nonTravelActivities[which(nonTravelActivities %in% allActivities)]

@@

```{r parameters, eval = FALSE, echo = FALSE}
parameters <- ddply(D, .(SEX, AGECAT), summarise,
             mean = mean(METs, na.rm=T),
             sd = sd(METs, na.rm=T)
             )

@@

```{r ITHIMObjs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, echo = FALSE, warning = FALSE}
upper <- 100
length <- 10

@@

D <- within(D,{
  State <- factor(State, levels = c("NC","TX","VA","FL","AZ","NY","CA","Natl."))
  Sex <- factor(Sex, levels = c("F","M"))
})

@@

```{r California, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
ITHIM.CA <- ITHIMList[["CA"]]
ITHIM.CA <- updateITHIM(ITHIM.CA, parName = "muNonTravel", 10)
ITHIM.national <- updateITHIM(ITHIM.national, parName = "muNonTravel", 10)
foo <- compareModels(ITHIM.national,ITHIM.CA)
foobar <- data.frame(cbind(melt(foo$daly.delta),paste0("ageClass",1:8)))
names(foobar) <- c("delta.DALY","Sex","Disease","ageClass")
p <- ggplot( foobar, aes(ageClass,-delta.DALY/1e3, fill = Sex) )
p + geom_bar(stat="identity", position = "dodge") + scale_x_discrete(name="Age Class", breaks = c(2,4,6,8)) + scale_y_continuous(name="DALYs Averted Nationwide (Thousands)") + facet_grid( . ~ Disease) + theme_bw() 
```

# Appendix

### 2016-09-27 manuscript/manuscript.tex
Switched to pdf format for figures
Minor updates to manuscript and figures
Switched to stratification by State
Created figure for California comparison

@@

\begin{figure}[t]
  \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig3}}
    \caption{Mean travel time by mode (walking/cycling) for each of
      the four regions with a decrease in DALYs
      $(\textrm{HHS01},\textrm{HHS02},\textrm{HHS09},\textrm{HHS10})$. The
      national means are displayed on the far right.  These four
      regions correspond to New England/NewYork and the West
      Coast.}\label{meanMatrices}
\end{figure}

@@

\begin{figure}[t]
    \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig1}}
    \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig2}}
    \caption{Change in total national DALYs for each regional
      transportation estimates.}\label{dalyFigure}
\end{figure}

>>>>

%% \begin{figure}[t]
%%     \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig1}}
%%     \caption{Map of HHS Regions and metropolitan areas}\label{HHSmap}
%% \end{figure}

@@

\begin{figure}[t]
    \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig2}}
    \caption{Change in total national DALYs for each regional
      transportation estimates.}\label{dalyFigure}
\end{figure}

@@

\begin{figure}[t]
  \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig3.pdf}}
    \caption{Mean travel time by mode (walking/cycling) for each of
      the four regions with a decrease in DALYs
      $(\textrm{HHS01},\textrm{HHS02},\textrm{HHS09},\textrm{HHS10})$. The
      national means are displayed on the far right.  These four
      regions correspond to New England/NewYork and the West
      Coast. The age classes are defined as in the original ITHIM
      implementation using 8 eight age classes defined in terms of
      years as follows: 1. 0--4, 2. 5--14, 3. 15--29, 4. 30--44,
      5. 45--59, 6. 60--69, 7. 70--79, and 8. 80+. Age class 1 is
      omitted from all calclulations in this paper due to lack of
      data.}\label{meanMatrices}
\end{figure}

\begin{figure}[t]
  \centerline{\includegraphics[width=0.5\textwidth]{./figures/fig4.pdf}}
    \caption{California}\label{California}
\end{figure}
